Appendix S1

### 2020-12-01 analysis/paper/appendix/appendix_s1.Rmd
ensured that the Figures section starts on a new page, and the first figure is on that page as well.

---
title: "Appendix S1"
subtitle: "Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@merck.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@merck.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: false
  - Sarah L. Hoffmann:
      email: Sarah.Hoffmann@merck.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@merck.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      toc: no
      always_allow_html: true
      number_sections: FALSE
      fig_height: 7
      fig_width: 6
      reference_docx: "../../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks.lua
      - --lua-filter=../../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      toc: no
      number_sections: FALSE
      geometry: margin=1in
      latex_engine: "xelatex"
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks2.lua
      - --lua-filter=../../templates/pagebreak.lua
      includes:
        in_header: ../../templates/header_appendixS.tex
    bookdown::html_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      number_sections: FALSE
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks.lua
      - --lua-filter=../../templates/pagebreak.lua
fontsize: 12pt
mainfont: Times New Roman
bibliography:
- ../references.bib
- ../packages.bib
csl: "../../templates/ecological-applications.csl" # Insert path for the bib-style
---

@@

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../../figures/appendix/",
  dpi = 600,
  appendix = TRUE
)
```

@@

# Figures

```{r mine-facet-fig, fig.cap = 'Barplots of MIC statistics, faceted by habitat category.'}
mine_res %>%
  mutate(MetricCategory = recode(MetricCategory,
                                 'ChannelUnit' = 'Channel\nUnit',
                                 'SideChannel' = 'Side\nChannel',
                                 'WaterQuality' = 'Water\nQuality')) %>%
  ggplot(aes(x = Name,
             y = MIC)) +
  geom_col(fill = 'blue') +
  coord_flip() +
  facet_wrap(~ MetricCategory,
             scales = 'free_y',
             ncol = 2) +
  theme(legend.position = 'bottom',
        axis.text = element_text(size = 5))
```

>>>>

---
title: "Appendix S1"
subtitle: "Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models"
author:
  - Kevin E. See:
      email: Kevin.See@merck.com
      institute: [biomark]
      correspondence: true
  - Michael W. Ackerman:
      email: Mike.Ackerman@merck.com
      institute: [biomark]
      correspondence: false
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: false
  - Sarah L. Hoffmann:
      email: Sarah.Hoffmann@merck.com
      institute: [biomark]
      correspondence: false
  - Chris Beasley:
      email: Chris.Beasley@merck.com
      institute: [biomark]
      correspondence: false
institute:
  - biomark: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    bookdown::pdf_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      toc: no
      number_sections: FALSE
      geometry: margin=1in
      latex_engine: "xelatex"
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks2.lua
      - --lua-filter=../../templates/pagebreak.lua
      includes:
        in_header: ../../templates/header_appendixS.tex
    bookdown::word_document2:
      fig_caption: yes
      toc: no
      always_allow_html: true
      number_sections: FALSE
      fig_height: 7
      fig_width: 6
      reference_docx: "../../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks.lua
      - --lua-filter=../../templates/pagebreak.lua
    bookdown::html_document2:
      fig_caption: yes
      fig_height: 8.5
      fig_width: 6.5
      number_sections: FALSE
      pandoc_args:
      - --lua-filter=../../templates/scholarly-metadata.lua
      - --lua-filter=../../templates/author-info-blocks.lua
      - --lua-filter=../../templates/pagebreak.lua
fontsize: 12pt
mainfont: Times New Roman
bibliography:
- ../references.bib
- ../packages.bib
csl: "../../templates/ecological-applications.csl" # Insert path for the bib-style
---

@@

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../../figures/appendix/",
  dpi = 400,
  appendix = TRUE
)
```

@@

\newpage
# Figures

```{r mine-facet-fig, fig.height = 6.7, fig.cap = 'Barplots of MIC statistics, faceted by habitat category.'}
mine_res %>%
  mutate(MetricCategory = recode(MetricCategory,
                                 'ChannelUnit' = 'Channel\nUnit',
                                 'SideChannel' = 'Side\nChannel',
                                 'WaterQuality' = 'Water\nQuality')) %>%
  ggplot(aes(x = Name,
             y = MIC)) +
  geom_col(fill = 'blue') +
  coord_flip() +
  facet_wrap(~ MetricCategory,
             scales = 'free_y',
             ncol = 2) +
  theme(legend.position = 'bottom',
        axis.text = element_text(size = 5))
```
